\LARGE \bf My Paper Title

### 2016-12-11 source/conclusion.tex
-- Refactored into separate files. -- Added another reference.
More references and another table
Referencing sections, tables, and figures
Using global variables
Sorting citations
Added a rotated image and one that spans both columns

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Appendix file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Appendix}
\label{sec:appendix}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Conclusion file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
\label{sec:conclusion}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy \cite{knuth-website}.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

As noted in sections
\ref{sec:discussion_figures} and
\ref{sec:discussion_equations}
we have all work and no play making Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

\subsection{Important Stuff}
\label{sec:conclusions_important_stuff}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy
\cite{einstein-electrodynamics,
knuth-website,
knuth-fundamental-algorithms,
dirac-quantum-mechanics}.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

\subsection{Really Important Stuff}
\label{sec:conclusions_really_important_stuff}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
Figure \ref{fig:rotated_shapes} shows how we can rotate a graphic.

% A figure using an EPS vector image file.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth, angle =90]{../figures/shapes.eps}
\caption{Rotated EPS file.}
\label{fig:rotated_shapes}
\end{figure}

### 2016-12-11 source/discussion/figures.tex
Added a rotated image and one that spans both columns

% A figure.
\begin{figure}[h]
\centering
\includegraphics{../figures/shapes.eps}
\caption{Made with LibreOffice and saved as EPS.}
\label{fig:shapes}
\end{figure}

@@

% A figure.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/mountains.jpg}
\caption{Misty Mountains from Unsplash It \cite{unsplash}.}
\label{fig:mountains}
\end{figure}

@@

% A figure.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/lake.jpg}
\caption{A Mountain Lake from Unsplash It \cite{unsplash}.}
\label{fig:lake}
\end{figure}

>>>>

% A figure using an EPS vector image file.
\begin{figure}[h]
\centering
\includegraphics{../figures/shapes.eps}
\caption{Made with LibreOffice and saved as EPS.}
\label{fig:shapes}
\end{figure}

@@

% A figure using a JPG raster image file.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/mountains.jpg}
\caption{Misty Mountains from Unsplash It \cite{unsplash}.}
\label{fig:mountains}
\end{figure}

@@

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
Figure \ref{fig:outdoor_cafe} demonstrates how we can make an image span both columns.

% A figure that spans both columns.
\begin{figure*}[h]
\centering
\includegraphics[width=\textwidth,natwidth=800,natheight=600]{../figures/outdoor_cafe.jpg}
\caption{Outdoor Cafe from Unsplash It \cite{unsplash}.}
\label{fig:outdoor_cafe}
\end{figure*}
